Mixture distribution data generation

### 2022-02-14 Ch3_samplesize/Datagen_viz.Rmd
individual densities

### PLOT the mixture components -------------------------------
lnorm_densities <- purrr::map(1:4, function(y) stat_function(fun = dlnorm,
                                                             args = list(meanlog = mus[y], sdlog = sigsqs[y]),
                              color = dens_cols[y], size=1))
ggplot() +
  lnorm_densities +
  theme_minimal() +
  labs(y = "Density") +
  lims(x = c(0, 150)) +
  #scale_y_sqrt(limits = c(0, NA)) +
  NULL -> densities_plot
densities_plot

@@

indiv_densities <- purrr::map(1:nrow(indiv_pars), function(y) stat_function(fun = dlnorm,
                                                             args = list(meanlog = indiv_pars$mu[y], sdlog = indiv_pars$sigsq[y]),
                              color = dens_cols[indiv_pars$sgroup[y]], size=1, alpha = 0.5))
ggplot() +
  indiv_densities +
  lnorm_densities +
  theme_minimal() +
  labs(y = "Density") +
  lims(x = c(0, 150)) +
  #scale_y_sqrt(limits = c(0, NA)) +
  NULL -> indiv_densities
indiv_densities

>>>>

### PLOT the mixture components -------------------------------
lnorm_densities <- purrr::map(1:ngroup, function(y) stat_function(fun = dlnorm,
                                                             args = list(meanlog = mus[y], sdlog = sigsqs[y]),
                              color = dens_cols[y], size=1))
ggplot() +
  lnorm_densities +
  theme_minimal() +
  labs(y = "Density") +
  lims(x = c(0, 150)) +
  #scale_y_sqrt(limits = c(0, NA)) +
  NULL -> densities_plot
densities_plot

@@

indiv_densities <- purrr::map(1:nrow(indiv_pars), function(y) stat_function(fun = dlnorm,
                                                             args = list(meanlog = indiv_pars$mu[y], sdlog = indiv_pars$sigsq[y]),
                              color = dens_cols[indiv_pars$sgroup[y]], size=1, alpha = 0.3))
ggplot() +
  indiv_densities +
  lnorm_densities +
  theme_minimal() +
  labs(y = "Density") +
  lims(x = c(0, 150)) +
  #scale_y_sqrt(limits = c(0, NA)) +
  NULL -> indiv_densities
indiv_densities
